Red-Giant Hot Jupiters: Brilliant Radio Emitter?

### 2015-04-24 ms.tex
P_radio and F_nu are nomalized at 5AU, not 5.2AU.

It is illustrative to compare radio emission power of canonical hot jupiters and that of red giant hot jupiters. We adopt canonical values for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}. Then, equation (\ref{eq:Pkinp}) can be re-normalized as 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 220 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
&\approx & 2.2 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
&\approx & 100 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \\
\end{eqnarray}
%%%
\memoYF{what is the typical wind velocity of AGB stars?}
Thus, the jupiters to the AGB stars are intrinsically 200 times as bright as canonical hot Jupiters. In other words, we could search for radio signal from these stars in $(\sqrt{200})^3 \approx 3000$ times as large volume as the canonical hot jupiters.

We now turn to the spectral radio flux observed at the Earth. 
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
%&=& P_{\rm radio,\,J} \\
&\approx & 5\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3}  \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} \\
&\approx & 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5.2~\mbox{AU}} \right)^{-4/3} %\\
%&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\
%&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1} \left( \frac{R_p}{R_{p, J}} \right)^{3}
\end{eqnarray}
%%%
Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griebmeier2007} \memoYF{cite original paper!}.

>>>>

It is illustrative to compare radio emission power of canonical hot jupiters and that of red giant hot jupiters. We adopt canonical values for planetary mass, orbital distance, and orbital period of each type as shown in Table \ref{tab:comp_HJ}. Then, equation (\ref{eq:Pkinp}) can be re-normalized as 
%%%
\begin{eqnarray}
P_{\rm k,\,inp} 
&\approx & 230 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \\
&\approx & 2.3 \times 10^4 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{10^9 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \\
&\approx & 100 ~P_{\rm k,\,inp,\,J} \left( \frac{\mathcal{M}}{0.1\mathcal{M}_J} \right)^{2/3} \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \left( \frac{a}{0.05~\mbox{AU}} \right)^{-4/3} \\
\end{eqnarray}
%%%
\memoYF{what is the typical wind velocity of AGB stars?}
Thus, the jupiters to the AGB stars are intrinsically 200 times as bright as canonical hot Jupiters. In other words, we could search for radio signal from these stars in $(\sqrt{200})^3 \approx 3000$ times as large volume as the canonical hot jupiters.

We now turn to the spectral radio flux observed at the Earth. 
%%%
\begin{eqnarray}
F_{\nu} &=& \frac{P_{\rm radio}}{\Omega d^2 f_{\rm cyclotron}} \\
%&=& P_{\rm radio,\,J} \\
&\approx & 5.3\times 10^{-8} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
&& \times \left( \frac{\dot M}{\dot M_{\odot}} \right)^{2/3} \left( \frac{v}{v_{\odot}} \right)^{5/3} \\
&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3}  \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} \\
&\approx & 1.0 \times 10^{-5} \mbox{Jy} \left( \frac{d}{100\mbox{~pc}} \right)^{-2}  \\
&& \times \left( \frac{\dot M}{10^6 \dot M_{\odot}} \right)^{2/3} \left( \frac{v}{10^{-1} v_{\odot}} \right)^{5/3} \\
&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1/3} \left( \frac{a}{5~\mbox{AU}} \right)^{-4/3} %\\
%&\approx &  10^{-3} \mbox{Jy} \left( \frac{P_{\rm radio}}{200 P_{\rm radio, J}} \right) \left( \frac{l}{10\mbox{~pc}} \right)^{-2} \\
%&&\times \left( \frac{\mathcal{M}}{\mathcal{M}_J} \right)^{-1} \left( \frac{R_p}{R_{p, J}} \right)^{3}
\end{eqnarray}
%%%
Here, we used $P_{\rm radio,\,J}=2.1\times 10^{11}\mbox{~W}$ \citep{griebmeier2007} \memoYF{cite original paper!}.
